---
title: "Practise2"
author: "cscientist"
date: "December 31, 2016"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE, results="hide")
```

```{r simulatedata}
x<-rnorm(100); y<-x+rnorm(100,sd=0.5)
```

## R Markdown

Here is list:  
  - first item is apple  
  - second item is orange  
  - third item is banana  
  - fourth item is pear  
  - fifth item is apricot  
  - sixth item is watermelon  
  - seventh item is flower  
  
  Ordered list:  
  1. first apple  
  2. second orange  
  3. third banana  
  4. fourth pear  
  5. fifth apricot

  Another list:  
  - flower  
  - cake  
  - juice


```{r showtable, results="asis"}
library(xtable)
library(datasets)
data(airquality)
fit<-lm(Ozone~Wind+Temp+Solar.R,data=airquality)
xt<-xtable(summary(fit))
print(xt,type="html")

```

  
### Thats all


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure}
plot(pressure)
str(pressure)


```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.